---
title: "Testing ChatGPT ggplot2 code"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
vignette: >
  %\VignetteIndexEntry{Testing ChatGPT ggplot2 code}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##", 
  eval = TRUE, 
  error = TRUE,
  out.width = "50%"
)
options(width = 40)
library(ggplot2)
library(tibble)
library(dplyr)
library(glue)
```

```{css, echo=FALSE}
div.main-container {
  max-width: 100% !important;
  margin: auto;
}
pre {
  overflow-x: auto;
  max-width: 75% !important;
}
pre code {
  word-wrap: normal !important;
  max-width: 75% !important;
  white-space: pre-wrap !important;
}
```

```{r}
library(ChatGPTtestR)
```

## Prompt: write code for writing a custom plotting function using `ggplot2`

### Response

> Sure! Here's an example of how to write a custom plotting function using `ggplot2`:

```{r my_plot-01, eval=FALSE}
library(datasets)
library(ggplot2)

# Define custom function
my_plot <- function(data, x_var, y_var) {
  # Create ggplot object
  plot_obj <- ggplot(data, aes(x = {{x_var}}, y = {{y_var}})) +
    geom_point() +
    labs(x = x_var, y = y_var, title = "My Custom Plot")
  
  # Return plot object
  return(plot_obj)
}

# Example usage with built-in dataset
my_data <- mtcars
my_plot(my_data, mpg, wt)
```

> In this example, the `my_plot()` function takes three arguments: `data` (the data.frame to plot), `x_var` (the name of the x variable), and `y_var` (the name of the y variable).
>
> The function first creates a `ggplot` object with the specified x and y variables and adds a point geometry. It also adds labels to the x-axis, y-axis, and plot title.
>
> Finally, the function returns the `ggplot` object, which can be further customized or saved using the standard `ggplot2` syntax.
>
> In this example, we demonstrate the usage of the function by passing in the mtcars dataset and specifying the `mpg` and `wt` variables as the `x` and `y` variables, respectively.

### Test

```{r my_plot-test, eval=TRUE, error=TRUE}
library(datasets)
library(ggplot2)

# Define custom function
my_plot <- function(data, x_var, y_var) {
  # Create ggplot object
  plot_obj <- ggplot(data, aes(x = {{x_var}}, y = {{y_var}})) +
    geom_point() +
    labs(x = x_var, y = y_var, title = "My Custom Plot")
  
  # Return plot object
  return(plot_obj)
}

# Example usage with built-in dataset
my_data <- mtcars
my_plot(my_data, mpg, wt)
```

## Fix 

The correct implementation of this function requires knowledge of tidy-evaluation (for the variables passed to `ggplot2::aes()`). ChatGPT correctly defined the variables to `ggplot2::aes()`, but fell short of in it's implementation of the labels (with `ggplot2::labs()`). 

```{r plot_layer}
library(ggplot2)
plot_layer <- function(df, x_var, y_var, color_var, point_alpha) {
  # Create plot layer
    ggplot(data = df,
      mapping = ggplot2::aes(
        x = {{ x_var }}, 
        y = {{ y_var }}
        )
      ) +
      ggplot2::geom_point(
        ggplot2::aes(color = {{ color_var }}),
        alpha = point_alpha)
}
# Example usage with built-in dataset
ggp2_point_layer <- plot_layer(df = mpg, 
  x_var = displ, y_var = hwy, color_var = class,
  point_alpha = 0.33)
ggp2_point_layer
```


Now that we have the point layer working, we can write another function to create the labels layer:


```{r}
labs_layer <- function(points, xlab, ylab) {
  
  x_up <- toupper(deparse(substitute(xlab)))
  y_up <- toupper(deparse(substitute(ylab)))
  
  points + 
  ggplot2::labs(title = "My Better Custom Plot", 
    x = x_up, y = y_up)
}
labs_layer(points = ggp2_point_layer, 
  xlab = displ, ylab = hwy)
```

I can combine these into a single function, 

```{r}
point_plot <- function(data, xvar, yvar, hue, opac) {
  
  plot_layer <- function(df, x_var, y_var, color_var, point_alpha) {
  # Create plot layer
    ggplot(data = df,
      mapping = ggplot2::aes(
        x = {{ x_var }}, 
        y = {{ y_var }}
        )
      ) +
      ggplot2::geom_point(
        ggplot2::aes(color = {{ color_var }}),
        alpha = point_alpha)
  }
  
  ggp2_points <- plot_layer(df = data, 
                      x_var = xvar, y_var = yvar, 
                      color_var = hue, point_alpha = opac)
  # return(ggp2_points)
  
  labs_layer <- function(points, xlab, ylab) {

    x_up <- toupper(deparse(substitute(xlab)))
    y_up <- toupper(deparse(substitute(ylab)))

    points +
    ggplot2::labs(title = "My Better Custom Plot",
      x = x_up, y = y_up)
  }

  labs_layer(points = ggp2_points,
        xlab = xvar, ylab = yvar)
}
```

```{r}
point_plot(data = ggplot2::mpg,
  xvar = displ, yvar = hwy, 
  hue = class, opac = 0.33)
```




## Prompt: write code for a custom plotting function using `ggplot2` that includes a `geom_point()` and a `geom_line()`

### Response

> Sure! Here's an example of a custom plotting function using `ggplot2` that includes both `geom_point()` and `geom_line()`:

```{r , eval=FALSE}
library(ggplot2)

# Define custom function
my_plot <- function(data, x_var, y_var) {
  # Create ggplot object with both point and line geometries
  plot_obj <- ggplot(data, aes(x = {{x_var}}, y = {{y_var}})) +
    geom_point() +
    geom_line() +
    labs(x = x_var, y = y_var, title = "My Custom Plot")
  
  # Return plot object
  return(plot_obj)
}

# Example usage with built-in dataset
my_data <- mtcars
my_plot(my_data, mpg, wt)
```

> In this example, the `my_plot()` function takes three arguments: `data` (the data.frame to plot), `x_var` (the name of the x variable), and `y_var` (the name of the y variable).
>
> The function creates a `ggplot` object with both `geom_point()` and `geom_line()` geometries, adding labels to the x-axis, y-axis, and plot title.
>
> Finally, the function returns the `ggplot` object, which can be further customized or saved using the standard `ggplot2` syntax.
>
> In this example, we demonstrate the usage of the function by passing in the `mtcars` dataset and specifying the `mpg` and `wt` variables as the `x` and `y` variables, respectively. The resulting plot includes both point and line geometries, showing how the data points connect to each other.

### Test

```{r , eval=TRUE}
library(ggplot2)

# Define custom function
my_plot <- function(data, x_var, y_var) {
  # Create ggplot object with both point and line geometries
  plot_obj <- ggplot(data, aes(x = {{x_var}}, y = {{y_var}})) +
    geom_point() +
    geom_line() +
    labs(x = x_var, y = y_var, title = "My Custom Plot")
  
  # Return plot object
  return(plot_obj)
}

# Example usage with built-in dataset
my_data <- mtcars
my_plot(my_data, mpg, wt)
```
